\vfill A Survey of Web Testing Frameworks and a Workflow for Testing Javascript Applications

### 2014-05-10 Paper/paper.tex
Notes to myself, general fixes, commented out old notes

\subsection{What Has Been Done Already?}
Web developers are not clueless, they understand that there is a need for testing of web applications. Unfortunately, web development is still a relatively new domain and developers did not come together to work on the problem of testing but rather came up with their own proprietary solutions in isolation or merely on a per-project basis. Some of these tools gained traction and become larger, more general, tools.

\todo{What goes here?}
- Info info info

\subsubsection{Why It Is Insufficient}
- No standard
The problem that followed was that many of the tools attempted to remedy the same problems and so a developer would have to decide between a number of similar tools. Having to wade through a sea of similar tools is time-consuming and that can be the death of a cutting-edge application. The more time an application is off the market, the more time competitors have to develop their own versions. Yet another problem is that deciding between similar tools can be discouraging to the developer that just wants to write their application and test it quickly.

- Info info info

\subsection{Problems Still Faced/Why It's So Hard}
- A lot of products to test against (browsers)
Testing web applications is difficult. The web offers an impressive set of features, but with those features come some draw-backs. Two of the most frustrating drawbacks for developers are the number of platforms and the web's asynchronous nature.

@@

- Asynchronous shennanigans
The addition of Javascript to web applications led to a golden age of feature-rich applications with exciting UI that had not before been seen. This set of features and UI improvements came with an, albeit necessary, complication of asynchronous execution. Unlike traditional multi-threaded software, however, the developer is not given access to individual threads but is stuck with just the main thread. This sort of implementation is essential for dealing with asynchronous events like button clicks, data loading that doesn't hold up the web page, and a variety of other niceties, but is the cause of major headaches in testing. Without access to individual threads, the developer has to either write synchronous code that will be slow and not user-friendly, or rely on other mechanisms that allow code to be sequenced. Often it is hard to get code properly sequenced and it requires changing straightforward functions to a hideous amalgamation of callbacks.

@@

\subsection{Contributions of This Thesis}
- Framework
The goal of this thesis is to bring together tools that are already available for testing and combine them into a single framework that offers web application developers a single place to look for their testing needs. There are plenty of strong tools available and we hope to gather a subset of those tools to cover as much of testing spectrum as possible in an effort to save other developers time and energy in having to look at them all individually.
- Wade through all the tools currently out there
-- Focus in, no need to have every developer check out all 10000 tools
-- Weigh options

@@

- THIS NEEDS TO MOVE OR CHANGE SUBSECTION TO `WEB APPLICATIONS'
\subsubsection{Node.JS}
Node.JS, often called simply Node, is a JavaScript API for creating and running servers. ``Node's goal is to provide an easy way to build scalable network programs.'' \cite{Node} Node was created in 2009 and is sponsored by Joyent. Node does not use thread-based networking, instead opting for a single-threaded event loop and non-blocking I/O. Node allows developers to create and control web servers without the need for external software, such as Apache, commonly found in other sites.

@@

- TIE THIS CLIENT/SERVER STUFF into Web Applications, be specific, not generic
\subsection{Client/Server Architecture}
Web applications have a user-facing client-side and a ``rear-facing'' (IS THIS THE RIGHT TERM...) server-side.

@@

\subsection{Sample ToDo App}
In order to test out the various frameworks that we found online, we needed a small application with some functionality, but without the inherent complexity that was going to come with our evaluation application. After some searching, We decided upon a Todo application made with Express.js, Node.js, and MongoDB. \cite{ToDoAppHomePage} This application was selected because it included Node.js and had enough functionality that tests wouldn't be completely trivial while also not being overwhelming.
One of the challenges in testing that we quickly came across was the asynchronous nature of the MongoDB calls that were made in the sample app. Because of this headache, we will be discussing how the following frameworks deal with asynchronous test support as JavaScript is inherently asynchronous.
- Screenshots
- Example Navigation

@@

\subsection{Assumptions and Requirements}
In order to more thoroughly vet the many testing frameworks we came across, we had a number of assumptions about the projects we'd be looking at and requirements for those framework.
- Node.js server because it's JS, so it's testable.
- Something to do unit testing
- Something to do continuous integration

@@

- Node.js
- Browser based
- Javascript
- Database
- Open-source

\subsubsection{Tool Requirements \todo{Move this section elsewhere}}
Our requirements for the selection of testing tools was relatively simple. In addition to meeting the requirements of our ``average web application'', the only other requirement was that the tool was free. What ``free'' means is that the developer would have access to at the least the minimum functionality needed to use the tool on \emph{one} application that is \emph{open-source}. What we quickly found is that web testing tools love open-source projects but are far less willing to provide free functionality to private or closed-source projects. Occasionally the cost of tools will be discussed but in general we didn't review tools that did not offer a free option.
- Free

@@

More setup, more flexibility.
Better Async support.

@@

- TDD, BDD, Object methods
Intern uses Chai.js for assertion methods but has it built-in as opposed to Mocha in which you had to get it yourself. Again, this gives the developer access to Expect, Assert, and Object testing methods.

- Integration with Selenium
Intern uses the WebDriver API to communicate with Selenium to drive the automated broswer testing portion of Intern.

- Distinction between non-functional and functional tests
Intern's unit-test versus browser test seperation is termed, by Intern, nonfunctional versus functional testing. Nonfunctional tests are those that run without a browser while functional tests are WebDriver tests.

- Code Coverage!
Intern includes configurable code coverage metrics on your tests by default. Running unit tests gives the number of lines covered (ran) by the tests. Code coverage is provided by another Javascript library, Istanbul, created by Krishnan Anantheswaran \cite{Istanbul}.

@@

\todo{INCLUDE SELENIUM CODE TO DO THIS HERE}

Nightwatch does not, however, support unit-testing without the browser and therefore can only be used in combination with another testing tool.

@@

\subsubsection{PhantomJS\cite{PhantomJS}}
Too much.
- Really great though, could be useful if needed.
- Slow
- FULL DOM/Browser emulation

\subsubsection{ZombieJS\cite{ZombieJS}}
- Lightweight
- Headless
- NOT Full DOM emulation

@@

\subsection{Chosen Toolset}

- Unit Testing: Mocha w/ Chai
- Coverage: Istanbul
- CI: MagnumCI
- Browser Testing: Nightwatch
- Task Runner: Grunt
- Package Manager: NPM, Bower

@@

- Note OS X 'ulimit' issue with Grunt-watch

\subsection{Workflow}
- Unit Testing on save
- CI used for running browser tests

- 'Manually' instantiate Sauce Labs?

@@

\subsection{Our Setup}
- 15-inch MacBook Pro (Late 2008 model)
-- Processor  2.53 GHz Intel Core 2 Duo
-- Memory  4 GB 1067 MHz DDR3
-- Graphics  NVIDIA GeForce 9400M 256 MB
--- Not a particularly powerful computer, just your average everyday laptop.

- OS 10.9.2
-- Terminal
- Sublime w/ plugins
- Netbeans

@@

-- Extension to all of PX?
-- Extension to non-proprietary open-source project

@@

>>>>

\subsection{What Has Been Done Already?}
Web developers are not clueless, they understand that there is a need for testing of web applications. Unfortunately, web development is still a relatively new domain and developers have not come together to work on the problem of testing but rather have come up with their own proprietary solutions in isolation or merely on a per-project basis. Some of these tools have gained traction and become larger, more general, tools.

\todo{What goes here?}
\todo{Info info info}

\subsubsection{Why It Is Insufficient}
% - No standard
The problem that followed was that many of the tools attempted to remedy the same problems and so a developer would have to decide between a number of similar tools. Having to wade through a sea of similar tools is time-consuming and that can be the death of a cutting-edge application. The more time an application is off the market, the more time competitors have to develop their own versions. Yet another problem is that deciding between similar tools can be discouraging to the developer that just wants to write their application and test it quickly.

\todo{Info info info}

\subsection{Problems Still Faced/Why It's So Hard}
% - A lot of products to test against (browsers)
Testing web applications is difficult. The web offers an impressive set of features, but with those features come some draw-backs. Two of the most frustrating drawbacks for developers are the number of platforms and the web's asynchronous nature.

@@

% - Asynchronous shennanigans
The addition of Javascript to web applications led to a golden age of feature-rich applications with exciting UI that had not before been seen. This set of features and UI improvements came with an, albeit necessary, complication of asynchronous execution. Unlike traditional multi-threaded software, however, the developer is not given access to individual threads but is stuck with just the main thread. This sort of implementation is essential for dealing with asynchronous events like button clicks, data loading that doesn't hold up the web page, and a variety of other niceties, but is the cause of major headaches in testing. Without access to individual threads, the developer has to either write synchronous code that will be slow and not user-friendly, or rely on other mechanisms that allow code to be sequenced. Often it is hard to get code properly sequenced and it requires changing straightforward functions to a hideous amalgamation of callbacks.

@@

\subsection{Contributions of This Thesis}
%- Framework
The goal of this thesis is to bring together tools that are already available for testing and combine them into a single framework that offers web application developers a single place to look for their testing needs. There are plenty of strong tools available and we hope to gather a subset of those tools to cover as much of testing spectrum as possible in an effort to save other developers time and energy in having to look at them all individually.
%- Wade through all the tools currently out there
%-- Focus in, no need to have every developer check out all 10000 tools
%-- Weigh options

@@

\todo{THIS NEEDS TO MOVE OR CHANGE SUBSECTION TO `WEB APPLICATIONS'}
\subsubsection{Node.JS}
Node.JS, often called simply Node, is a JavaScript API for creating and running servers. ``Node's goal is to provide an easy way to build scalable network programs.'' \cite{Node} Node was created in 2009 and is sponsored by Joyent. Node does not use thread-based networking, instead opting for a single-threaded event loop and non-blocking I/O. Node allows developers to create and control web servers without the need for external software, such as Apache, commonly found in other sites.

@@

\todo{TIE THIS CLIENT/SERVER STUFF into Web Applications, be specific, not generic}
\subsection{Client/Server Architecture}
Web applications have a user-facing client-side and a ``rear-facing'' \todo{IS THIS THE RIGHT TERM...} server-side.

@@

\subsection{Sample ToDo App}
In order to test out the various frameworks that we found online, we needed a small application with some functionality, but without the inherent complexity that was going to come with our evaluation application. After some searching, We decided upon a Todo application made with Express.js, Node.js, and MongoDB. \cite{ToDoAppHomePage} This application was selected because it included Node.js and had enough functionality that tests wouldn't be completely trivial while also not being overwhelming.
One of the challenges in testing that we quickly came across was the asynchronous nature of the MongoDB calls that were made in the sample app. Because of this headache, we will be discussing how the following frameworks deal with asynchronous test support as JavaScript is inherently asynchronous.
\todo{- Screenshots}
\todo{- Example Navigation}

@@

\subsection{Assumptions and Requirements}
In order to more thoroughly vet the many testing frameworks we came across, we had a number of assumptions about the projects we'd be looking at and requirements for those framework.
%- Node.js server because it's JS, so it's testable.
%- Something to do unit testing
%- Something to do continuous integration

@@

%- Node.js
%- Browser based
%- Javascript
%- Database
%- Open-source

\subsubsection{Tool Requirements \todo{Move this section elsewhere}}
Our requirements for the selection of testing tools was relatively simple. In addition to meeting the requirements of our ``average web application'', the only other requirement was that the tool was free. What ``free'' means is that the developer would have access to at the least the minimum functionality needed to use the tool on \emph{one} application that is \emph{open-source}. What we quickly found is that web testing tools love open-source projects but are far less willing to provide free functionality to private or closed-source projects. Occasionally the cost of tools will be discussed but in general we didn't review tools that did not offer a free option.
%- Free

@@

%- More setup, more flexibility.
%- Better Async support.

@@

%- TDD, BDD, Object methods
Intern uses Chai.js for assertion methods but has it built-in as opposed to Mocha in which you had to get it yourself. Again, this gives the developer access to Expect, Assert, and Object testing methods.

%- Integration with Selenium
Intern uses the WebDriver API to communicate with Selenium to drive the automated broswer testing portion of Intern.

%- Distinction between non-functional and functional tests
Intern's unit-test versus browser test seperation is termed, by Intern, nonfunctional versus functional testing. Nonfunctional tests are those that run without a browser while functional tests are WebDriver tests.

%- Code Coverage!
Intern includes configurable code coverage metrics on your tests by default. Running unit tests gives the number of lines covered (ran) by the tests. Code coverage is provided by another Javascript library, Istanbul, created by Krishnan Anantheswaran \cite{Istanbul}.

@@

\begin{lstlisting}
var assert = require('chai').assert,
    test = require('selenium-webdriver/testing'),
    webdriver = require('selenium-webdriver');

test.describe('Google Search', function() {
  test.it('should work', function() {
    var driver = new webdriver.Builder().
        withCapabilities(webdriver.Capabilities.chrome()).
        build();

    driver.get('http://www.google.com');
    driver.findElement(webdriver.By.name('q')).sendKeys('nightwatch');
    driver.findElement(webdriver.By.name('btnG')).click();

    driver.sleep(1000);
    driver.findElement(webdriver.By.id('main')).getText().then(function (text) {
        assert.isTrue(text.indexOf("The Night Watch") !== -1);
        driver.quit();
    });
  });
});
\end{lstlisting}

In addition to being more verbose, I've had to add an assertion library and this code has to be run using Node.js and the Mocha module instead of using the Selenium command.

Nightwatch does not, however, support unit-testing without the browser and therefore can only be used in combination with another testing tool that supports unit-testing, such as Mocha, Jasmine, or any of the others outlined above.

@@

\subsubsection{PhantomJS\cite{PhantomJS}}
% Too much.
%- Really great though, could be useful if needed.
%- Slow
%- FULL DOM/Browser emulation

\subsubsection{ZombieJS\cite{ZombieJS}}
%- Lightweight
%- Headless
%- NOT Full DOM emulation

@@

\subsection{Chosen Toolset}
% - Unit Testing: Mocha w/ Chai
% - Coverage: Istanbul
% - CI: MagnumCI
% - Browser Testing: Nightwatch
% - Task Runner: Grunt
% - Package Manager: NPM, Bower

@@

% - Note OS X 'ulimit' issue with Grunt-watch

\subsection{Workflow}
% - Unit Testing on save
% - CI used for running browser tests

% - 'Manually' instantiate Sauce Labs?

@@

\subsection{Our Setup}
% - 15-inch MacBook Pro (Late 2008 model)
% -- Processor  2.53 GHz Intel Core 2 Duo
% -- Memory  4 GB 1067 MHz DDR3
% -- Graphics  NVIDIA GeForce 9400M 256 MB
% --- Not a particularly powerful computer, just your average everyday laptop.

% - OS 10.9.2
% -- Terminal
% - Sublime w/ plugins
% - Netbeans

@@

% -- Extension to all of PX?
% -- Extension to non-proprietary open-source project

@@

\subsection{ToDo App Test Code}

\subsection{PolyXpress Test Code}
